---
title: cliapp
output:
  github_document:
    toc: true
    toc_depth: 3
    includes:
      before_body: header.md
---

```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.path = "man/figures/"
)
```

## Superseded

This package is superseded, and we focus on the cli package now:
https://github.com/r-lib/cli

## Installation

```{r eval = FALSE}
install.packages("cliapp")
```

## Usage

This README uses the simple theme, included in the package, see
`?simple_theme()`.

```{r echo = FALSE, results = "hide"}
options(crayon.enabled = TRUE)
options(crayon.colors = 256)
crayon::num_colors(forget = TRUE)
options(cli.unicode = TRUE)
library(cliapp)
start_app(theme = simple_theme(), output = "stdout")
```

```r
library(cliapp)
start_app(theme = simple_theme())
```

### Headings

`cli_h1()`, `cli_h2()` and `cli_h3()` create three levels of headings:

```r
cli_h1("Title")
cli_h2("Subtitle")
cli_h3("Subsubtitle")
```

```{r headings, render=cliapp:::knit_print.html, echo = FALSE}
capture.output(cli_h1("Title"))
capture.output(cli_h2("Subtitle"))
capture.output(cli_h3("Subsubtitle"))
```

### Text and inline markup

All (non-verbatim) outputted text runs through `glue::glue()`. In addition
to glue interpolation, cliapp also supports inline markup via the
`{markup text}` form. The builtin theme defines inline markup classes,
see `?inline-markup`.

```r
cli_text("{emph Emphasized text}, {strong Strong} importance.
  A piece of code: {code  sum(a) / length(a)}. Package names:
  {pkg cliapp}, file names: {path /usr/bin/env}, etc.")
```

```{r inline-markup, render=cliapp:::knit_print.html, echo = FALSE}
capture.output(cli_text("{emph Emphasized text}, {strong Strong} importance.
  A piece of code: {code  sum(a) / length(a)}. Package names:
  {pkg cliapp}, file names : {path /usr/bin/env}, etc."))
```

### Alerts

```r
cli_alert("Generic alert")
cli_alert_danger("Something went horribly wrong")
cli_alert_warning("Better watch out!")
cli_alert_info("About to download 1.4GiB of data.")
cli_alert_success("All downloads finished successfully")
```

```{r alerts, render=cliapp:::knit_print.html, echo = FALSE}
capture.output(cli_alert("Generic alert"))
capture.output(cli_alert_danger("Something went horribly wrong"))
capture.output(cli_alert_warning("Better watch out!"))
capture.output(cli_alert_info("About to download 1.4GiB of data."))
capture.output(cli_alert_success("All downloads finished successfully"))
```

### Lists

Ordered, unordered and definition lists, they can be nested.
See `?cli_ol()`, `?cli_ul()`, `?cli_dl()` and `?cli_it()`.

```r
cli_div(theme = list(ol = list("margin-left" = 2)))
cli_ul("one", .close = FALSE)
cli_ol(c("foo", "bar", "foobar"))
cli_it("two")
cli_end()
cli_end()
```

```{r lists, render=cliapp:::knit_print.html, echo = FALSE}
capture.output({
cli_div(theme = list(ol = list("margin-left" = 2)))
cli_ul("one", .close = FALSE)
cli_ol(c("foo", "bar", "foobar"))
cli_it("two")
cli_end()
cli_end()
})
```

### Progress bars

Progress bars are supported via the
[progress package](https://github.com/r-lib/progress).

## License

MIT © RStudio
